---
title: "Indo"
author: "kamryn"
date: "2023-06-13"
output: html_document
---
```{r}
library(naniar)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
nd_gain_data <- read.csv("data/nd-gain-data/joined_data/nd-gain-joined.csv")
```

round value column for two numbers after the decimal
```{r}
nd_gain_data$value <- round(nd_gain_data$value, digits = 2)
```

select year
```{r}
nd_gain_data_2020 <- nd_gain_data %>%  
  filter(year== 2020)
```

example

```{r}
dataset_2020_wider_numeric <- dataset_2020_wider %>% 
  select(-ISO3, )
```

```{r}
dataset_2020_wider <- dataset_2020_wider %>% 
  mutate(sids_context = ifelse(sids_))
```
```{r}

```


pivot wider
```{r}
nd_gain_data_2020_wider <- nd_gain_data_2020 %>% 
  pivot_wider(names_from = indicator,
              values_from = value)
```



scatter plot
```{r}
ggplot(data = nd_gain_data_2020_wider, aes(x = education,
                                     y = human_development_index,
                                     color = sids_context)) +
  geom_point() + 
  geom_smooth() +
  labs(title = "Education and Human Development Index, ND-GAIN 2020",
       x = "education",
       y = "human develpment index") +
  theme_minimal()

```

```{r}
ggplot(data = nd_gain_data_2020_wider, aes(x = paved_roads,
                                           y = quality_of_trade_and_transport_infrastructure,
                                           color = sids_context)) +
  geom_point() +
  geom_smooth() +
  labs(title = "paved roads and quality of trade and transport infrastructure, ND-GAIN 2020",
       x = "paved roads",
       y = "quality of trade and transport infrastructure") +
  theme_minimal()
```

```{r}
nd_gain_joined_data <- nd_gain_data %>% 
  clean_names()
```

```{r}
table(nd_gain_data$iso3)
```


```{r}
medical_staff_data <- nd_gain_data %>% 
  filter(indicator=="medical_staff")
```


```{r}
paved_roads_data <- nd_gain_data %>% 
  filter(indicator=="paved_roads")
```


```{r}

ggplot(data = paved_roads_data, aes(x = value)) +
  geom_histogram()
```


```{r}

ggplot(data = medical_staff_data, aes(x = value)) +
  geom_histogram()
```


Now let's explore the relationships between our numeric columns in the dataset with a correlation matrix

Select numeric columns for correlations

```{r}
nd_gain_data_numeric <- nd_gain_data_2020_wider %>% select(-ISO3, -Name, -year, -sids_context, -innovation)
```

Create a correlation matrix

```{r}
cor_matrix <- cor(nd_gain_data_numeric[complete.cases(nd_gain_data_numeric), ], use = "pairwise.complete.obs")
```
```{r}
sum(is.na(dataset_2020_wider_sids_numeric$))
```


Plot the correlation matrix

```{r}
corrplot <- ggcorrplot(cor_matrix, type = "lower", outline.color = "white") +
  theme(axis.text.x = element_text(size = 3),
        axis.text.y = element_text(size = 3))
corrplot
```
Make the correlation plot interactive

```{r}
ggplot(data = penguins_data, aes(x = culmen_depth_mm,
                                 y = flipper_length_mm))
```

```{r}
ggplotly(corrplot)
```


fliter for just sids

```{r}
dataset_2020_wider_sids <- nd_gain_data_2020_wider %>% 
  filter(sids_context == "sids")
```

select only the numeric columns
```{r}
dataset_2020_wider_sids_numeric <- dataset_2020_wider_sids %>% 
  select(-ISO3, -Name, -year, -sids_context)
```

```{r}
cor_matrix <- cor(dataset_2020_wider_sids_numeric, use = "pairwise.complete.obs")
```
```{r}
corrplot <- ggcorrplot(cor_matrix, type = "lower", outline.color = "white") +
  theme(axis.text.x = element_text(size = 3),
        axis.text.y = element_text(size = 3))
corrplot
```

```{r}
ggplot(data = nd_gain_data_2020_wider, aes(x = paved_roads,
                                           y = quality_of_trade_and_transport_infrastructure,
                                           color = sids_context)) +
  geom_point() +
  geom_smooth() +
  labs(title = "paved roads and quality of trade and transport infrastructure, ND-GAIN 2020",
       x = "paved roads",
       y = "quality of trade and transport infrastructure") +
  theme_minimal()
```

